---
title: "Blade-level SEMs with meadow-scale predictors"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("R/helpers.R")
source("R/coefs.R")
# library(nlme)
library(lme4)
library(dplyr)
library(readr)
library(DHARMa)
library(ggplot2)
library(GGally)
library(optimx)
library(performance)

# load CRAN version of pSEM - 2.1.0
library(piecewiseSEM)
library(visreg)
library(multcompView)

```

SEMs to assess temperature, grazing, disease relationships. All data (2019 and 2021) from sites where available.  

SEMs are set up with meadow-scale predictors (e.g. epifauna abundance, canopy height) and modeled at the blade scale for lesion area, grazing scars, and blade area.  

Some relationships have been eliminated through the LMM/GLMM modeling (e.g. epifauna does not predict grazing)

Note, remove tidal height because it gets messy (missing "path" from tidal height to canopy, density even though they are measured at site level)

Different SEMs compared to answer specific questions:  
- does temperature afffect lesion area directly or indirectly?  
- does epifauna abundance or grazing influence lesion area directly? 
- does grazing drive disease or does disease drive grazing (i.e. increased grazing increases disease versus diseaed plants accumulating more grazing scars)

```{r data}
# data ###
dis <- read_csv("data/meadow_predictors_blade_SEM_data.csv")
dis$BladeAreaLog <- log10(dis$BladeArea)
dis$BladeArea_cm2 <- dis$BladeArea/100
dis$fTransect <- as.factor(dis$Transect)
dis$sLatitude <- scale(dis$Latitude)
site <- select(dis, c(Epifauna, CanopyHeight, DensityLog, TempAnomWarm_May, Latitude, sLatitude,
                      TempAnomWarm_April, TempAnomWarm_June, MonthlyMeanTemp_June, YearBinary, Meadow, Region))
site <- distinct(site)
dis2 <- subset(dis, LesionArea>0)
dis2$LesionAreaLog <- log10(dis2$LesionArea)
```

## Lesion Area models

#### full model
```{r}
les1 <- psem(
  lmer(Epifauna ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         CanopyHeight + DensityLog 
       + YearBinary +
         (1|Meadow) + (1|Region),
       data=dis2),
  lmer(CanopyHeight ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=dis2),
  lmer(DensityLog ~ TempAnomWarm_June + MonthlyMeanTemp_June +
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=dis2),
  glmer(GrazingScars ~ CanopyHeight + DensityLog + 
          BladeAreaLog +  
          TempAnomWarm_June + MonthlyMeanTemp_June + 
          YearBinary + 
          (1|Region) + (1|Meadow),
        data=dis2,
        family = "binomial"),
  lmer(BladeAreaLog ~ Epifauna + CanopyHeight + DensityLog + 
         TempAnomWarm_June + MonthlyMeanTemp_June +
         YearBinary +
         (1|Region) + (1|Meadow),
       data=dis2),
lmer(LesionAreaLog ~ GrazingScars + BladeAreaLog + Epifauna + DensityLog + CanopyHeight + 
               TempAnomWarm_June + MonthlyMeanTemp_June +
                YearBinary + (1|Meadow) + (1|Region),
             data=dis2),
  DensityLog%~~%CanopyHeight
)
summary(les1)
coefs(les1)
```

Passes global fit (p=0.68), AIC = 108.898 Lesion area has grazing and epifauna links, no temp effect significant

#### alternative model - no temp to lesion
```{r }
les2 <- psem(
  lmer(Epifauna ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         CanopyHeight + DensityLog 
       + YearBinary +
         (1|Meadow) + (1|Region),
       data=dis2),
  lmer(CanopyHeight ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=dis2),
  lmer(DensityLog ~ TempAnomWarm_June + MonthlyMeanTemp_June +
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=dis2),
  glmer(GrazingScars ~ CanopyHeight + DensityLog + 
          BladeAreaLog +  
          TempAnomWarm_June + MonthlyMeanTemp_June + 
          YearBinary + 
          (1|Region) + (1|Meadow),
        data=dis2,
        family = "binomial"),
  lmer(BladeAreaLog ~ Epifauna + CanopyHeight + DensityLog + 
         TempAnomWarm_June + MonthlyMeanTemp_June +
          YearBinary +
         (1|Region) + (1|Meadow),
       data=dis2),
lmer(LesionAreaLog ~ GrazingScars + BladeAreaLog + Epifauna + DensityLog + CanopyHeight + 
                YearBinary + (1|Meadow) + (1|Region),
             data=dis2),
  DensityLog%~~%CanopyHeight
)
summary(les2)
# coefs(les2)
```

Does not pass global fit test (p = 0.02). AIC = 119.006. D-sep shows temp effects on lesion area are missing and significant.

#### alternative model - no temp to grazing
```{r}
les3 <- psem(
  lmer(Epifauna ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         CanopyHeight + DensityLog 
       + YearBinary +
         (1|Meadow) + (1|Region),
       data=dis2),
  lmer(CanopyHeight ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=dis2),
  lmer(DensityLog ~ TempAnomWarm_June + MonthlyMeanTemp_June +
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=dis2),
  glmer(GrazingScars ~ CanopyHeight + DensityLog + 
          BladeAreaLog +  
           YearBinary + 
          (1|Region) + (1|Meadow),
        data=dis2,
        family = "binomial"),
  lmer(BladeAreaLog ~ Epifauna + CanopyHeight + DensityLog + 
         TempAnomWarm_June + MonthlyMeanTemp_June +
          YearBinary +
         (1|Region) + (1|Meadow),
       data=dis2),
lmer(LesionAreaLog ~ GrazingScars + BladeAreaLog + Epifauna + DensityLog + CanopyHeight + 
       TempAnomWarm_June + MonthlyMeanTemp_June +
                YearBinary + (1|Meadow) + (1|Region),
             data=dis2),
  DensityLog%~~%CanopyHeight
)
summary(les3)
# coefs(les3)
```

Doesn't pass global test (p=0), AIC = 192.544. Temp effects on grazing scars are missing

#### alternative model - no grazing to lesion
```{r les4}
les4 <- psem(
  lmer(Epifauna ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         CanopyHeight + DensityLog 
       + YearBinary +
         (1|Meadow) + (1|Region),
       data=dis2),
  lmer(CanopyHeight ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         YearBinary +  
         (1|Meadow) + (1|Region),
       data=dis2),
  lmer(DensityLog ~ TempAnomWarm_June + MonthlyMeanTemp_June +
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=dis2),
  glmer(GrazingScars ~ CanopyHeight + DensityLog + 
          BladeAreaLog +  
          TempAnomWarm_June + MonthlyMeanTemp_June + 
          YearBinary + 
          (1|Region) + (1|Meadow),
        data=dis2,
        family = "binomial"),
  lmer(BladeAreaLog ~ Epifauna + CanopyHeight + DensityLog + 
         TempAnomWarm_June + MonthlyMeanTemp_June +
          YearBinary +
         (1|Region) + (1|Meadow),
       data=dis2),
lmer(LesionAreaLog ~ BladeAreaLog + Epifauna + DensityLog + CanopyHeight + 
               TempAnomWarm_June + MonthlyMeanTemp_June +
                YearBinary + (1|Meadow) + (1|Region),
             data=dis2),
  DensityLog%~~%CanopyHeight
)
summary(les4)
```

Doesn't pass (p=0.02), AIC= 117.449, d-sep shows need for grazing to lesion

#### alternative model - no epifauna to lesion
```{r les5}
les5 <- psem(
  lmer(Epifauna ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         CanopyHeight + DensityLog 
       + YearBinary +
         (1|Meadow) + (1|Region),
       data=dis2),
  lmer(CanopyHeight ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         YearBinary +  
         (1|Meadow) + (1|Region),
       data=dis2),
  lmer(DensityLog ~ TempAnomWarm_June + MonthlyMeanTemp_June +
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=dis2),
  glmer(GrazingScars ~ CanopyHeight + DensityLog + 
          BladeAreaLog +  
          TempAnomWarm_June + MonthlyMeanTemp_June + 
           YearBinary + 
          (1|Region) + (1|Meadow),
        data=dis2,
        family = "binomial"),
  lmer(BladeAreaLog ~ Epifauna + CanopyHeight + DensityLog + 
         TempAnomWarm_June + MonthlyMeanTemp_June +
         YearBinary +
         (1|Region) + (1|Meadow),
       data=dis2),
lmer(LesionAreaLog ~ GrazingScars + BladeAreaLog + DensityLog + CanopyHeight + 
               TempAnomWarm_June + MonthlyMeanTemp_June +
               YearBinary + (1|Meadow) + (1|Region),
             data=dis2),
  DensityLog%~~%CanopyHeight
)
summary(les5)
```

Fails global fit test (p=0.002), AIC = 123.318 D-sep  indicates need for epifauna to lesion area  

#### alternative model - reverse direction from lesion to grazing

```{r les6}
les6 <- psem(
  lmer(Epifauna ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         CanopyHeight + DensityLog 
       + YearBinary +
         (1|Meadow) + (1|Region),
       data=dis2),
  lmer(CanopyHeight ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         YearBinary +  
         (1|Meadow) + (1|Region),
       data=dis2),
  lmer(DensityLog ~ TempAnomWarm_June + MonthlyMeanTemp_June +
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=dis2),
  glmer(GrazingScars ~ CanopyHeight + DensityLog + 
          BladeAreaLog +  LesionAreaLog +
          TempAnomWarm_June + MonthlyMeanTemp_June + 
           YearBinary + 
          (1|Region) + (1|Meadow),
        data=dis2,
        family = "binomial"),
  lmer(BladeAreaLog ~ Epifauna + CanopyHeight + DensityLog + 
         TempAnomWarm_June + MonthlyMeanTemp_June +
         YearBinary +
         (1|Region) + (1|Meadow),
       data=dis2),
lmer(LesionAreaLog ~  BladeAreaLog + Epifauna + DensityLog + CanopyHeight + 
               TempAnomWarm_June + MonthlyMeanTemp_June +
                YearBinary + (1|Meadow) + (1|Region),
             data=dis2),
  DensityLog%~~%CanopyHeight
)
summary(les6)
```

Passes global fit (p=0.478). AIC = 109.475 (slightly higher than for the original model)

#### alternative model - lesion and grazing are correlated errors
```{r les7}
les7 <- psem(
  lmer(Epifauna ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         CanopyHeight + DensityLog 
       + YearBinary +
         (1|Meadow) + (1|Region),
       data=dis2),
  lmer(CanopyHeight ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=dis2),
  lmer(DensityLog ~ TempAnomWarm_June + MonthlyMeanTemp_June +
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=dis2),
  glmer(GrazingScars ~ CanopyHeight + DensityLog + 
          BladeAreaLog +  
          TempAnomWarm_June + MonthlyMeanTemp_June + 
          YearBinary + 
          (1|Region) + (1|Meadow),
        data=dis2,
        family = "binomial"),
  lmer(BladeAreaLog ~ Epifauna + CanopyHeight + DensityLog + 
         TempAnomWarm_June + MonthlyMeanTemp_June +
          YearBinary +
         (1|Region) + (1|Meadow),
       data=dis2),
lmer(LesionAreaLog ~ BladeAreaLog + Epifauna + DensityLog + CanopyHeight + 
               TempAnomWarm_June + MonthlyMeanTemp_June +
                YearBinary + (1|Meadow) + (1|Region),
             data=dis2),
  LesionAreaLog%~~%GrazingScars,
  DensityLog%~~%CanopyHeight
)
summary(les7)
coefs(les7)
```

Passes global test p=0.638, AIC = 106.898 Exactly 2 less than global model.

```{r}
df.AIC <- data.frame(model=c("les1", "les2", "les3", "les4", "les5", "les6", "les7"),
                     AIC=c(108.898, 119.006, 192.544, 117.449, 123.318, 109.475, 106.898))
df.AIC$deltaAIC <- df.AIC$AIC-min(df.AIC$AIC)
df.AIC$likelihood <- exp(-df.AIC$deltaAIC/2)
df.AIC$weight <- df.AIC$likelihood/sum(df.AIC$likelihood)
tibble(df.AIC)
```

