---
title: "Grazing Scar direction SEM results"
output: github_document
---

```{r setup, include=FALSE}
library(here)
source(here("R/helpers.R"))
source(here("R/coefs.R"))
library(nlme)
library(lme4)
library(dplyr)
library(readr)
library(DHARMa)
library(ggplot2)
library(GGally)
library(optimx)
library(performance)
library(piecewiseSEM)
library(effects)
library(ggeffects)
library(kableExtra)
```

# Simple SEMs to asses direction of grazing to disease relationship

Strictly assessing three variables - disease (prevalence or lesion area), leaf area (log-transformed), and grazing scar presence/absence. Also using tidal height as it affects leaf area (and gives more flexiblity to the SEM). Random effects are site and region. 

Testing two possiblities - direction from grazing to disease or from disease to grazing. 

```{r data}
# data ###
dis <- read_csv("data/epiphyte_SEM_data_all_large.csv")
# same data as for complex SEM because no grazing scars in 2020 except WA
dis$BladeAreaLog <- log10(dis$BladeArea)
dis_gz <- select(dis, c(Year, Meadow, Region, Blade, BladeAreaLog, TidalHeightBinary, YearBinary, GrazingScars, Prevalence, LesionArea))
dis_gz1 <- na.omit(dis_gz)
dis_gz1$Meadow_Year <- paste(dis_gz1$Meadow, dis_gz1$Year, sep="_")
print("meadow-year combos in prevalence SEM")
length(unique(dis_gz1$Meadow_Year))
unique(dis_gz1$Meadow_Year)
print("nrows of disease data (sample size)")
nrow(dis_gz1)
```

## Prevalence - grazing to disease

```{r prev_gz_mod}
sem_prev_gz <- psem(
  lmer(BladeAreaLog ~ TidalHeightBinary + YearBinary + 
         (1|Region) + (1|Meadow),
       data=dis_gz1),
  glmer(GrazingScars ~ BladeAreaLog + 
           YearBinary + 
          (1|Region) + (1|Meadow),
        data=dis_gz1,
        family = "binomial"),
  glmer(Prevalence ~ BladeAreaLog + GrazingScars +
          TidalHeightBinary + YearBinary + 
          (1|Region) + (1|Meadow),
        data=dis_gz1,
        family = "binomial")
)
summary(sem_prev_gz, conserve = T)
```

```{r prev_gz_coefs}
coefs(sem_prev_gz)
```

## Prevalence - disease to grazing
```{r prev_dis_mod}
sem_prev_dis <- psem(
  lmer(BladeAreaLog ~ TidalHeightBinary + YearBinary + 
         (1|Region) + (1|Meadow),
       data=dis_gz1),
  glmer(GrazingScars ~ BladeAreaLog + Prevalence + 
           YearBinary + 
          (1|Region) + (1|Meadow),
        data=dis_gz1,
        family = "binomial"),
  glmer(Prevalence ~ BladeAreaLog +
          TidalHeightBinary + YearBinary + 
          (1|Region) + (1|Meadow),
        data=dis_gz1,
        family = "binomial")
)
summary(sem_prev_dis)
```

```{r prev_dis_coefs}
coefs(sem_prev_dis)
```

AIC is greater for dis --> gz (40.78) vs gz --> dis (37.06) - suggests that the gz --> disease model better fits the data. Standardized coefficients are similar (0.2227 vs 0.2672); p-values are equivalent (0.0000). Positive relationship - either disease infection increases likelihood of grazing, or presence of grazing increases likelihood of disease. Based on the AIC improvement, there is some evidence for more support for the pathway from grazing to disease. 

## Lesion area - grazing to disease

```{r les_dat}
les_gz <- subset(dis_gz1, LesionArea>0)
les_gz$LesionAreaLog <- log10(les_gz$LesionArea)
les_gz <- na.omit(les_gz)

print("sample size for lesion models")
nrow(les_gz)
```

```{r les_dis_mod}
sem_les_dis <- psem(
  lmer(BladeAreaLog ~ TidalHeightBinary + YearBinary +
         (1|Region) + (1|Meadow),
       data=les_gz),
  glmer(GrazingScars ~ BladeAreaLog + 
          YearBinary + 
          (1|Region) + (1|Meadow),
        data=les_gz,
        family = "binomial"),
  lmer(LesionAreaLog ~ BladeAreaLog + GrazingScars + 
          TidalHeightBinary + YearBinary + 
          (1|Region) + (1|Meadow),
        data=les_gz)
)
summary(sem_les_dis)
```


```{r}
coefs(sem_les_dis)
```

## Lesion area - disease to grazing

```{r les_gz_mod}
sem_les_gz <- psem(
  lmer(BladeAreaLog ~ TidalHeightBinary + YearBinary +
         (1|Region) + (1|Meadow),
       data=les_gz),
  glmer(GrazingScars ~ BladeAreaLog + LesionAreaLog + 
          YearBinary + 
          (1|Region) + (1|Meadow),
        data=les_gz,
        family = "binomial"),
  lmer(LesionAreaLog ~ BladeAreaLog + 
          TidalHeightBinary + YearBinary + 
          (1|Region) + (1|Meadow),
        data=les_gz)
)
summary(sem_les_gz)
```

```{r}
coefs(sem_les_gz)
```

AIC is equivalent between the two models for lesion area. Standardized estimate is slightly larger for dis --> gz (0.15) compared to gz --> dis (0.12). P-values are small and equivalent for both (0.0038 vs 0.0026). No strong evidence in support of either direction. 

Note however that the relationship is positive (i.e. larger lesions make grazing more likely/grazing makes lesions larger). Given this, it seems perhaps more biologically likely that lesions make grazing more likely? 
