---
title: "Community Interaction SEM results"
output: github_document
---

```{r setup, include=FALSE}
library(here)
source(here("R/helpers.R"))
source(here("R/coefs.R"))
library(nlme)
library(lme4)
library(dplyr)
library(readr)
library(DHARMa)
library(ggplot2)
library(GGally)
library(optimx)
library(performance)
library(piecewiseSEM)
library(effects)
```

# SEMs comparing epifauna vs lacuna vs ampithoid

```{r data}
# data ###
dis <- read_csv("data/epiphyte_SEM_data.csv")
dis$BladeAreaLog <- log10(dis$BladeArea)
# use the full data set without subsetting because the SEM no longer includes epiphytes or grazing
dis1 <- select(dis, c(Epifauna, TempAnomWarm_June, MonthlyMeanTemp_June, CanopyHeight, DensityLog, YearBinary, Year, Meadow, Region,
                      BladeAreaLog, TidalHeightBinary, Prevalence, LesionArea, Lacuna, Ampithoid, Idoteid))
```

## Prevalence + Epifauna

```{r prev1}
dis2 <- select(dis1, -c(Lacuna, Ampithoid, Idoteid))
dis2 <- na.omit(dis2)
sem_prev_epi <- psem(
  lmer(Epifauna ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         CanopyHeight + DensityLog +
         YearBinary +
         (1|Meadow) + (1|Region),
       data=dis2),
  lmer(CanopyHeight ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=dis2),
  lmer(DensityLog ~ TempAnomWarm_June + MonthlyMeanTemp_June +
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=dis2),
    lmer(BladeAreaLog ~ Epifauna + CanopyHeight + DensityLog + 
         TempAnomWarm_June + MonthlyMeanTemp_June +
         TidalHeightBinary + YearBinary +
         (1|Region) + (1|Meadow),
       data=dis2),
  glmer(Prevalence ~ BladeAreaLog + Epifauna + CanopyHeight + DensityLog + 
          TempAnomWarm_June + MonthlyMeanTemp_June + 
          TidalHeightBinary + YearBinary + 
          (1|Region) + (1|Meadow),
        data=dis2,
        family = "binomial"),
  DensityLog%~~%CanopyHeight
)
summary(sem_prev_epi)

```

Model passes global fit. Epifauna is positive and significant predictor for Prevalence. 

```{r}
coefs(sem_prev_epi)
```


## prev + lac

```{r}
dis3 <- select(dis1, -c(Epifauna, Ampithoid, Idoteid))
dis3 <- dis3[-which(is.na(dis3$Lacuna)),] # omit missing Lacuna values
dis3 <- na.omit(dis3) # remove any other NAs (missing blade area for one)

sem_prev_lac <- psem(
  lmer(Lacuna ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         CanopyHeight + DensityLog 
       + YearBinary +
         (1|Meadow) + (1|Region),
       data=dis3),
  lmer(CanopyHeight ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=dis3),
  lmer(DensityLog ~ TempAnomWarm_June + MonthlyMeanTemp_June +
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=dis3),
  lmer(BladeAreaLog ~ Lacuna + CanopyHeight + DensityLog + 
         TempAnomWarm_June + MonthlyMeanTemp_June +
         TidalHeightBinary + YearBinary +
         (1|Region) + (1|Meadow),
       data=dis3),
  glmer(Prevalence ~ BladeAreaLog + Lacuna + CanopyHeight + DensityLog + 
          TempAnomWarm_June + MonthlyMeanTemp_June +
          TidalHeightBinary + YearBinary + 
          (1|Region) + (1|Meadow),
        data=dis3,
        family = "binomial"),
  DensityLog%~~%CanopyHeight
)
summary(sem_prev_lac)

```
Passes global fit test
Lacuna effect on Prevalence is sig and positive

```{r}
coefs(sem_prev_lac)
```

## prev + amp

```{r}
dis4 <- select(dis1, -c(Epifauna, Lacuna, Idoteid))
dis4 <- dis4[-which(is.na(dis4$Ampithoid)),] # omit missing Ampithoid values
dis4 <- na.omit(dis4) # remove any other NAs (missing blade area for one)

sem_prev_amp <- psem(
  lmer(Ampithoid ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         CanopyHeight + DensityLog 
       + YearBinary +
         (1|Meadow) + (1|Region),
       data=dis4),
  lmer(CanopyHeight ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=dis4),
  lmer(DensityLog ~ TempAnomWarm_June + MonthlyMeanTemp_June +
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=dis4),
  lmer(BladeAreaLog ~ Ampithoid + CanopyHeight + DensityLog + 
         TempAnomWarm_June + MonthlyMeanTemp_June +
         TidalHeightBinary + YearBinary +
         (1|Region) + (1|Meadow),
       data=dis4),
  glmer(Prevalence ~ BladeAreaLog + Ampithoid + CanopyHeight + DensityLog + 
          TempAnomWarm_June + MonthlyMeanTemp_June +
          TidalHeightBinary + YearBinary + 
          (1|Region) + (1|Meadow),
        data=dis4,
        family = "binomial"),
  DensityLog%~~%CanopyHeight
)
summary(sem_prev_amp)

```

Passes global fit test. Ampithoid is negative for prevalence

```{r}
coefs(sem_prev_amp)
```

## prev + idoteid

```{r}
dis5 <- select(dis1, -c(Epifauna, Lacuna, Ampithoid))
dis5 <- dis5[-which(is.na(dis5$Idoteid)),] # omit missing Ampithoid values
dis5 <- na.omit(dis5) # remove any other NAs (missing blade area for one)

sem_prev_ido <- psem(
  lmer(Idoteid ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         CanopyHeight + DensityLog 
       + YearBinary +
         (1|Meadow) + (1|Region),
       data=dis5),
  lmer(CanopyHeight ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=dis5),
  lmer(DensityLog ~ TempAnomWarm_June + MonthlyMeanTemp_June +
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=dis5),
  lmer(BladeAreaLog ~ Idoteid + CanopyHeight + DensityLog + 
         TempAnomWarm_June + MonthlyMeanTemp_June +
         TidalHeightBinary + YearBinary +
         (1|Region) + (1|Meadow),
       data=dis5),
  glmer(Prevalence ~ BladeAreaLog + Idoteid + CanopyHeight + DensityLog + 
          TempAnomWarm_June + MonthlyMeanTemp_June +
          TidalHeightBinary + YearBinary + 
          (1|Region) + (1|Meadow),
        data=dis5,
        family = "binomial"),
  DensityLog%~~%CanopyHeight
)
summary(sem_prev_ido)

```

Passes global fit test. Idoteid is significant and negative for prevalence. 

```{r}
coefs(sem_prev_ido)
```

```{r}
multigroup(sem_prev_ido, group = "Region")
```

## Limit to complete cases (sites with lacuna and ampithoids)

### epifauna
```{r cc_epi}

dis_cc <- na.omit(dis1) # remove missing Epifauna, Lacuna, and Ampithoid values, plus any other NAs (missing blade area for one)

sem_prev_epi_cc <- psem(
  lmer(Epifauna ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         CanopyHeight + DensityLog +
         YearBinary +
         (1|Meadow) + (1|Region),
       data=dis_cc),
  lmer(CanopyHeight ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=dis_cc),
  lmer(DensityLog ~ TempAnomWarm_June + MonthlyMeanTemp_June +
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=dis_cc),
    lmer(BladeAreaLog ~ Epifauna + CanopyHeight + DensityLog + 
         TempAnomWarm_June + MonthlyMeanTemp_June +
         TidalHeightBinary + YearBinary +
         (1|Region) + (1|Meadow),
       data=dis_cc),
  glmer(Prevalence ~ BladeAreaLog + Epifauna + CanopyHeight + DensityLog + 
          TempAnomWarm_June + MonthlyMeanTemp_June + 
          TidalHeightBinary + YearBinary + 
          (1|Region) + (1|Meadow),
        data=dis_cc,
        family = "binomial"),
  DensityLog%~~%CanopyHeight
)
summary(sem_prev_epi_cc)

```

Passes global fit test. Epifauna is positive and significant for prevalence. 

Standardized coefs of sem:

```{r}
coefs(sem_prev_epi_cc)
```
### lacuna
```{r cc_lac}

sem_prev_lac_cc <- psem(
  lmer(Lacuna ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         CanopyHeight + DensityLog 
       + YearBinary +
         (1|Meadow) + (1|Region),
       data=dis_cc),
  lmer(CanopyHeight ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=dis_cc),
  lmer(DensityLog ~ TempAnomWarm_June + MonthlyMeanTemp_June +
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=dis_cc),
  lmer(BladeAreaLog ~ Lacuna + CanopyHeight + DensityLog + 
         TempAnomWarm_June + MonthlyMeanTemp_June +
         TidalHeightBinary + YearBinary +
         (1|Region) + (1|Meadow),
       data=dis_cc),
  glmer(Prevalence ~ BladeAreaLog + Lacuna + CanopyHeight + DensityLog + 
          TempAnomWarm_June + MonthlyMeanTemp_June +
          TidalHeightBinary + YearBinary + 
          (1|Region) + (1|Meadow),
        data=dis_cc,
        family = "binomial"),
  DensityLog%~~%CanopyHeight
)
summary(sem_prev_lac_cc)


```

Passes global fit test. Lacuna is positive and sig for prevalence.

```{r}
coefs(sem_prev_lac_cc)
```

### ampithoid
```{r}
sem_prev_amp_cc <- psem(
  lmer(Ampithoid ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         CanopyHeight + DensityLog 
       + YearBinary +
         (1|Meadow) + (1|Region),
       data=dis_cc),
  lmer(CanopyHeight ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=dis_cc),
  lmer(DensityLog ~ TempAnomWarm_June + MonthlyMeanTemp_June +
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=dis_cc),
  lmer(BladeAreaLog ~ Ampithoid + CanopyHeight + DensityLog + 
         TempAnomWarm_June + MonthlyMeanTemp_June +
         TidalHeightBinary + YearBinary +
         (1|Region) + (1|Meadow),
       data=dis_cc),
  glmer(Prevalence ~ BladeAreaLog + Ampithoid + CanopyHeight + DensityLog + 
          TempAnomWarm_June + MonthlyMeanTemp_June +
          TidalHeightBinary + YearBinary + 
          (1|Region) + (1|Meadow),
        data=dis_cc,
        family = "binomial"),
  DensityLog%~~%CanopyHeight
)
summary(sem_prev_amp_cc)
```

Passes global fit test. Ampithoid is negative for prevalence. Epiphyte presence not sig for prevalence

```{r}
coefs(sem_prev_amp_cc)
```

## Lesion + Epifauna
```{r les_dat}
les1 <- subset(dis1, LesionArea>0)
les1$LesionAreaLog <- log10(les1$LesionArea)
```

```{r}

les2 <- select(les1, -c(Lacuna, Ampithoid, Idoteid))
les2 <- na.omit(les2)
sem_les_epi <- psem(
  lmer(Epifauna ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         CanopyHeight + DensityLog +
         YearBinary +
         (1|Meadow) + (1|Region),
       data=les2),
  lmer(CanopyHeight ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=les2),
  lmer(DensityLog ~ TempAnomWarm_June + MonthlyMeanTemp_June +
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=les2),
    lmer(BladeAreaLog ~ Epifauna + CanopyHeight + DensityLog + 
         TempAnomWarm_June + MonthlyMeanTemp_June +
         TidalHeightBinary + YearBinary +
         (1|Region) + (1|Meadow),
       data=les2),
  lmer(LesionAreaLog ~ BladeAreaLog + Epifauna + CanopyHeight + DensityLog + 
          TempAnomWarm_June + MonthlyMeanTemp_June + 
          TidalHeightBinary + YearBinary + 
          (1|Region) + (1|Meadow),
        data=les2),
  DensityLog%~~%CanopyHeight
)
summary(sem_les_epi)
```

Passes global fit test. Epifauna is sig and pos for Lesion Area
Standardized coefs:

```{r}
coefs(sem_les_epi)
```

## Lesion + Lacuna
```{r}
les3 <- select(les1, -c(Epifauna, Ampithoid, Idoteid))
les3 <- na.omit(les3)
sem_les_lac <- psem(
  lmer(Lacuna ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         CanopyHeight + DensityLog +
         YearBinary +
         (1|Meadow) + (1|Region),
       data=les3),
  lmer(CanopyHeight ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=les3),
  lmer(DensityLog ~ TempAnomWarm_June + MonthlyMeanTemp_June +
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=les3),
    lmer(BladeAreaLog ~ Lacuna + CanopyHeight + DensityLog + 
         TempAnomWarm_June + MonthlyMeanTemp_June +
         TidalHeightBinary + YearBinary +
         (1|Region) + (1|Meadow),
       data=les3),
  lmer(LesionAreaLog ~ BladeAreaLog + Lacuna + CanopyHeight + DensityLog + 
          TempAnomWarm_June + MonthlyMeanTemp_June + 
          TidalHeightBinary + YearBinary + 
          (1|Region) + (1|Meadow),
        data=les3),
  DensityLog%~~%CanopyHeight
)
summary(sem_les_lac)
```
Passes global fit test. Lacuna is sig and pos for Lesion Area
Standardized coefs:

```{r}
coefs(sem_les_lac)
```

## Lesion + Ampithoid
```{r}
les4 <- select(les1, -c(Epifauna, Lacuna, Idoteid))
les4 <- na.omit(les4)
sem_les_amp <- psem(
  lmer(Ampithoid ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         CanopyHeight + DensityLog +
         YearBinary +
         (1|Meadow) + (1|Region),
       data=les4),
  lmer(CanopyHeight ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=les4),
  lmer(DensityLog ~ TempAnomWarm_June + MonthlyMeanTemp_June +
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=les4),
    lmer(BladeAreaLog ~ Ampithoid + CanopyHeight + DensityLog + 
         TempAnomWarm_June + MonthlyMeanTemp_June +
         TidalHeightBinary + YearBinary +
         (1|Region) + (1|Meadow),
       data=les4),
  lmer(LesionAreaLog ~ BladeAreaLog + Ampithoid + CanopyHeight + DensityLog + 
          TempAnomWarm_June + MonthlyMeanTemp_June + 
          TidalHeightBinary + YearBinary + 
          (1|Region) + (1|Meadow),
        data=les4),
  DensityLog%~~%CanopyHeight
)
summary(sem_les_amp)
```

Passes global fit test. Ampithoid is significant and negative for lesion area
Standarized coefs:

```{r}
coefs(sem_les_amp)
```
## Lesion + Idoteid 

```{r}
les5 <- select(les1, -c(Epifauna, Lacuna, Ampithoid))
les5 <- na.omit(les5)
sem_les_ido <- psem(
  lmer(Idoteid ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         CanopyHeight + DensityLog +
         YearBinary +
         (1|Meadow) + (1|Region),
       data=les5),
  lmer(CanopyHeight ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=les5),
  lmer(DensityLog ~ TempAnomWarm_June + MonthlyMeanTemp_June +
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=les5),
    lmer(BladeAreaLog ~ Idoteid + CanopyHeight + DensityLog + 
         TempAnomWarm_June + MonthlyMeanTemp_June +
         TidalHeightBinary + YearBinary +
         (1|Region) + (1|Meadow),
       data=les5),
  lmer(LesionAreaLog ~ BladeAreaLog + Idoteid + CanopyHeight + DensityLog + 
          TempAnomWarm_June + MonthlyMeanTemp_June + 
          TidalHeightBinary + YearBinary + 
          (1|Region) + (1|Meadow),
        data=les5),
  DensityLog%~~%CanopyHeight
)
summary(sem_les_ido)
```

Passes global fit test. Idoteid is NOT significant for Lesion Area, though coefficient is positive. 

```{r}
coefs(sem_les_ido)
```


## Complete cases 

```{r}
# limit to complete cases of lesion data
les_cc <- subset(dis_cc, LesionArea>0)
les_cc$LesionAreaLog <- log10(les_cc$LesionArea)
```

### CC lesion + Epifauna

```{r}
sem_les_epi_cc <- psem(
  lmer(Epifauna ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         CanopyHeight + DensityLog +
         YearBinary +
         (1|Meadow) + (1|Region),
       data=les_cc),
  lmer(CanopyHeight ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=les_cc),
  lmer(DensityLog ~ TempAnomWarm_June + MonthlyMeanTemp_June +
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=les_cc),
    lmer(BladeAreaLog ~ Epifauna + CanopyHeight + DensityLog + 
         TempAnomWarm_June + MonthlyMeanTemp_June +
         TidalHeightBinary + YearBinary +
         (1|Region) + (1|Meadow),
       data=les_cc),
  lmer(LesionAreaLog ~ BladeAreaLog + Epifauna + CanopyHeight + DensityLog + 
          TempAnomWarm_June + MonthlyMeanTemp_June + 
          TidalHeightBinary + YearBinary + 
          (1|Region) + (1|Meadow),
        data=les_cc),
  DensityLog%~~%CanopyHeight
)
summary(sem_les_epi_cc)
```
Passes global fit test. Epifauna is sig and pos for Lesion area

```{r}
coefs(sem_les_epi_cc)

```

### CC lesion + Lacuna

```{r}
sem_les_lac_cc <- psem(
  lmer(Lacuna ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         CanopyHeight + DensityLog +
         YearBinary +
         (1|Meadow) + (1|Region),
       data=les_cc),
  lmer(CanopyHeight ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=les_cc),
  lmer(DensityLog ~ TempAnomWarm_June + MonthlyMeanTemp_June +
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=les_cc),
    lmer(BladeAreaLog ~ Lacuna + CanopyHeight + DensityLog + 
         TempAnomWarm_June + MonthlyMeanTemp_June +
         TidalHeightBinary + YearBinary +
         (1|Region) + (1|Meadow),
       data=les_cc),
  lmer(LesionAreaLog ~ BladeAreaLog + Lacuna + CanopyHeight + DensityLog + 
          TempAnomWarm_June + MonthlyMeanTemp_June + 
          TidalHeightBinary + YearBinary + 
          (1|Region) + (1|Meadow),
        data=les_cc),
  DensityLog%~~%CanopyHeight
)
summary(sem_les_lac_cc)
```
Passes global fit test. Lacuana is sig and positive for lesion area
Standardized coefs:

```{r}
coefs(sem_les_lac_cc)
```

### CC lesion + ampithoid
```{r}
sem_les_amp_cc <- psem(
  lmer(Ampithoid ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         CanopyHeight + DensityLog +
         YearBinary +
         (1|Meadow) + (1|Region),
       data=les_cc),
  lmer(CanopyHeight ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=les_cc),
  lmer(DensityLog ~ TempAnomWarm_June + MonthlyMeanTemp_June +
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=les_cc),
    lmer(BladeAreaLog ~ Ampithoid + CanopyHeight + DensityLog + 
         TempAnomWarm_June + MonthlyMeanTemp_June +
         TidalHeightBinary + YearBinary +
         (1|Region) + (1|Meadow),
       data=les_cc),
  lmer(LesionAreaLog ~ BladeAreaLog + Ampithoid + CanopyHeight + DensityLog + 
          TempAnomWarm_June + MonthlyMeanTemp_June + 
          TidalHeightBinary + YearBinary + 
          (1|Region) + (1|Meadow),
        data=les_cc),
  DensityLog%~~%CanopyHeight
)
summary(sem_les_amp_cc)
```

Passes global fit test. Ampithoid is sig and negative for lesion area.

```{r}
coefs(sem_les_amp_cc)
```

## SEM Conclusions
- Epifauna abundance influences disease  
- Lacuna and ampithoid abundance show contrasting effects, could be explained by contrasting mechanisms  
- Limited mediation of temperature effects  

# Partial Residuals
Use models that include all cases (not complete case data), plot partial residuals of epifauna, lacuana, and ampithoid for disease response variables (prevalence and lesion area)

## Prevalence
```{r}
# approach from Duffy 2015 - doesn't work for binomial glmm
# create list of models for prev ~ epifauna
# pre_epi_model <- list(glm(Prevalence ~ BladeAreaLog + Epifauna + CanopyHeight + DensityLog + 
#           TempAnomWarm_June + MonthlyMeanTemp_June + 
#           TidalHeightBinary + YearBinary, 
#           # random=~1|Region/Meadow,
#         data=dis2,
#         family="binomial"))
# try <- partialResid(Prevalence ~ Epifauna, pre_epi_model)
# PrevalenceResidY <- resid(glmer(Prevalence ~ BladeAreaLog + CanopyHeight + DensityLog + 
#           TempAnomWarm_June + MonthlyMeanTemp_June + 
#           TidalHeightBinary + YearBinary +
#             (1|Region) +(1|Meadow), 
#         data=dis2,
#         family="binomial"))
# EpifaunaResidX <- resid(lmer(Epifauna ~ BladeAreaLog + CanopyHeight + DensityLog + 
#           TempAnomWarm_June + MonthlyMeanTemp_June + 
#           TidalHeightBinary + YearBinary +
#             (1|Region) +(1|Meadow), 
#         data=dis2))
# plot(exp(PrevalenceResidY)~EpifaunaResidX)
# alternative is using the effects package
prev_epi_1 <- glmer(Prevalence ~ BladeAreaLog + Epifauna + CanopyHeight + DensityLog + 
          TempAnomWarm_June + MonthlyMeanTemp_June + 
          TidalHeightBinary + YearBinary +
            (1|Region) +(1|Meadow), 
        data=dis2,
        family="binomial")
plot(predictorEffect("Epifauna", prev_epi_1, partial.residuals=TRUE))
# will want to try and get the year/site means plotted onto this plot, but can hold off for now?
prev_lac_1 <- glmer(Prevalence ~ BladeAreaLog + Lacuna + CanopyHeight + DensityLog + 
          TempAnomWarm_June + MonthlyMeanTemp_June + 
          TidalHeightBinary + YearBinary +
            (1|Region) +(1|Meadow), 
        data=dis3,
        family="binomial")
plot(predictorEffect("Lacuna", prev_lac_1, partial.residuals=TRUE))

prev_amp_1 <- glmer(Prevalence ~ BladeAreaLog + Ampithoid + CanopyHeight + DensityLog + 
          TempAnomWarm_June + MonthlyMeanTemp_June + 
          TidalHeightBinary + YearBinary +
            (1|Region) +(1|Meadow), 
        data=dis4,
        family="binomial")
plot(predictorEffect("Ampithoid", prev_amp_1,partial.residuals=TRUE))

prev_ido_1 <- glmer(Prevalence ~ BladeAreaLog + Idoteid + CanopyHeight + DensityLog + 
          TempAnomWarm_June + MonthlyMeanTemp_June + 
          TidalHeightBinary + YearBinary +
            (1|Region) +(1|Meadow), 
        data=dis5,
        family="binomial")

plot(predictorEffect("Idoteid", prev_ido_1,partial.residuals=TRUE))

```

## Lesion
### Epifauna
```{r}
# have to re-specify the model using lme() because partialResid() doens't work with lmer()
les_epi_model <- list(lesion=lme(LesionAreaLog ~ BladeAreaLog + Epifauna + CanopyHeight + DensityLog + 
          TempAnomWarm_June + MonthlyMeanTemp_June + 
          TidalHeightBinary + YearBinary, 
          random=~1|Region/Meadow,
        data=les2))
les_epi_resid <- partialResid(LesionAreaLog ~ Epifauna, modelList=les_epi_model)
les_epi_resid_df <- cbind(les2, EpifaunaResidX=les_epi_resid$xresid, LesionResidY=les_epi_resid$yresid)
les_epi_resid_summ <- les_epi_resid_df %>%
  group_by(Year, Meadow)%>%
  summarise(EpifaunaResidX_Meadow=mean(EpifaunaResidX),
            LesionResidY_Meadow=mean(LesionResidY))
ggplot()+
  geom_point(data=les_epi_resid,aes(x=xresid,y=yresid),size=2.5,alpha=0.75,col="grey50")+
  stat_smooth(data=les_epi_resid,aes(x=xresid,y=yresid),method="lm",se=F,lwd=1,col="black")+
  geom_point(data=les_epi_resid_summ, aes(x=EpifaunaResidX_Meadow, y=LesionResidY_Meadow, color=as.factor(Year)),
             size=3)+
  scale_color_discrete(name="Year")+
  labs(x="Log Epifauna | others",y="Log Lesion Area | others",nrow=2)+
  theme_bw(base_size=18)+
  guides(col=guide_legend(ncol=2))+
  theme(panel.grid.major=element_blank(),panel.grid.minor=element_blank())

# coefs(les_epi_1)
# plot(les_epi_resid)
# les_epi_resid <- partialResid(LesionAreaLog ~ Epifauna + (1|Meadow) + (1|Region), modelList = sem_les_epi)
# les_yresid <- resid(lmer(LesionAreaLog ~ BladeAreaLog + CanopyHeight + DensityLog + 
#           TempAnomWarm_June + MonthlyMeanTemp_June + 
#           TidalHeightBinary + YearBinary + 
#           (1|Region) + (1|Meadow),
#         data=les2))
# les_xresid <- resid(lmer(Epifauna ~ BladeAreaLog + CanopyHeight + DensityLog + 
#           TempAnomWarm_June + MonthlyMeanTemp_June + 
#           TidalHeightBinary + YearBinary + 
#           (1|Region) + (1|Meadow),
#         data=les2))
# plot(les_xresid, les_yresid)
```


```{r}
# re-set sem as all lme()
sem_les_epi_1 <- psem(
  lme(Epifauna ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         CanopyHeight + DensityLog +
         YearBinary,
      random=~1|Region/Meadow,
       data=les2),
  lme(CanopyHeight ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         YearBinary,
      random=~1|Region/Meadow,
       data=les2),
  lme(DensityLog ~ TempAnomWarm_June + MonthlyMeanTemp_June +
         YearBinary,
      random=~1|Region/Meadow,
       data=les2),
    lme(BladeAreaLog ~ Epifauna + CanopyHeight + DensityLog + 
         TempAnomWarm_June + MonthlyMeanTemp_June +
         TidalHeightBinary + YearBinary,
      random=~1|Region/Meadow,
       data=les2),
  lme(LesionAreaLog ~ BladeAreaLog + Epifauna + CanopyHeight + DensityLog + 
          TempAnomWarm_June + MonthlyMeanTemp_June + 
          TidalHeightBinary + YearBinary,  
      random=~1|Region/Meadow,
        data=les2),
  DensityLog%~~%CanopyHeight
)

les_epi_resid_1 <- partialResid(LesionAreaLog ~ Epifauna, modelList=sem_les_epi_1)
les_epi_resid1_df <- cbind(les2, EpifaunaResidX=les_epi_resid_1$xresid, LesionResidY=les_epi_resid_1$yresid)
les_epi_resid1_summ <- les_epi_resid1_df %>%
  group_by(Year, Meadow)%>%
  summarise(EpifaunaResidX_Meadow=mean(EpifaunaResidX),
            LesionResidY_Meadow=mean(LesionResidY))
ggplot()+
  geom_point(data=les_epi_resid_1,aes(x=xresid,y=yresid),size=2.5,alpha=0.75,col="grey50")+
  stat_smooth(data=les_epi_resid_1,aes(x=xresid,y=yresid),method="lm",se=F,lwd=1,col="black")+
  geom_point(data=les_epi_resid1_summ, aes(x=EpifaunaResidX_Meadow, y=LesionResidY_Meadow, color=as.factor(Year)),
             size=3)+
  scale_color_discrete(name="Year")+
  labs(x="Log Epifauna | others",y="Log Lesion Area | others",nrow=2)+
  theme_bw(base_size=18)+
  guides(col=guide_legend(ncol=2))+
  theme(panel.grid.major=element_blank(),panel.grid.minor=element_blank())


```

### Lacuna
```{r}
# have to re-specify the model using lme() because partialResid() doens't work with lmer()
les_lac_model <- list(lesion=lme(LesionAreaLog ~ BladeAreaLog + Lacuna + CanopyHeight + DensityLog + 
          TempAnomWarm_June + MonthlyMeanTemp_June + 
          TidalHeightBinary + YearBinary, 
          random=~1|Region/Meadow,
        data=les3))
les_lac_resid <- partialResid(LesionAreaLog ~ Lacuna, modelList=les_lac_model)
les_lac_resid_df <- cbind(les3, LacunaResidX=les_lac_resid$xresid, LesionResidY=les_lac_resid$yresid)
les_lac_resid_summ <- les_lac_resid_df %>%
  group_by(Year, Meadow)%>%
  summarise(LacunaResidX_Meadow=mean(LacunaResidX),
            LesionResidY_Meadow=mean(LesionResidY))
ggplot()+
  geom_point(data=les_lac_resid,aes(x=xresid,y=yresid),size=2.5,alpha=0.75,col="grey50")+
  stat_smooth(data=les_lac_resid,aes(x=xresid,y=yresid),method="lm",se=F,lwd=1,col="black")+
  geom_point(data=les_lac_resid_summ, aes(x=LacunaResidX_Meadow, y=LesionResidY_Meadow, color=as.factor(Year)),
             size=3)+
  scale_color_discrete(name="Year")+
  labs(x="Log Lacuna | others",y="Log Lesion Area | others",nrow=2)+
  theme_bw(base_size=18)+
  guides(col=guide_legend(ncol=2))+
  theme(panel.grid.major=element_blank(),panel.grid.minor=element_blank())
```

### Ampithoid
```{r}
# have to re-specify the model using lme() because partialResid() doens't work with lmer()
les_amp_model <- list(lesion=lme(LesionAreaLog ~ BladeAreaLog + Ampithoid + CanopyHeight + DensityLog + 
          TempAnomWarm_June + MonthlyMeanTemp_June + 
          TidalHeightBinary + YearBinary, 
          random=~1|Region/Meadow,
        data=les4))
les_amp_resid <- partialResid(LesionAreaLog ~ Ampithoid, modelList=les_amp_model)
les_amp_resid_df <- cbind(les4, AmpithoidResidX=les_amp_resid$xresid, LesionResidY=les_amp_resid$yresid)
les_amp_resid_summ <- les_amp_resid_df %>%
  group_by(Year, Meadow)%>%
  summarise(AmpithoidResidX_Meadow=mean(AmpithoidResidX),
            LesionResidY_Meadow=mean(LesionResidY))
ggplot()+
  geom_point(data=les_amp_resid,aes(x=xresid,y=yresid),size=2.5,alpha=0.75,col="grey50")+
  stat_smooth(data=les_amp_resid,aes(x=xresid,y=yresid),method="lm",se=F,lwd=1,col="black")+
  geom_point(data=les_amp_resid_summ, aes(x=AmpithoidResidX_Meadow, y=LesionResidY_Meadow, color=as.factor(Year)),
             size=3)+
  scale_color_discrete(name="Year")+
  labs(x="Log Ampithoid | others",y="Log Lesion Area | others",nrow=2)+
  theme_bw(base_size=18)+
  guides(col=guide_legend(ncol=2))+
  theme(panel.grid.major=element_blank(),panel.grid.minor=element_blank())
```

Alternatively, use the effects package and look at partial correlations using effect plot

```{r}

les_epi_1 <- lmer(LesionAreaLog ~ BladeAreaLog + Epifauna + CanopyHeight + DensityLog + 
          TempAnomWarm_June + MonthlyMeanTemp_June + 
          TidalHeightBinary + YearBinary +
            (1|Region) +(1|Meadow), 
        data=les2)
plot(predictorEffect("Epifauna", les_epi_1, partial.residuals=TRUE))


les_lac_1 <- lmer(LesionAreaLog ~ BladeAreaLog + Lacuna + CanopyHeight + DensityLog + 
          TempAnomWarm_June + MonthlyMeanTemp_June + 
          TidalHeightBinary + YearBinary +
            (1|Region) +(1|Meadow), 
        data=les3)
plot(predictorEffect("Lacuna", les_lac_1, partial.residuals=TRUE))


les_amp_1 <- lmer(LesionAreaLog ~ BladeAreaLog + Ampithoid + CanopyHeight + DensityLog + 
          TempAnomWarm_June + MonthlyMeanTemp_June + 
          TidalHeightBinary + YearBinary +
            (1|Region) +(1|Meadow), 
        data=les4)
plot(predictorEffect("Ampithoid", les_amp_1, partial.residuals=TRUE))


les_ido_1 <- lmer(LesionAreaLog ~ BladeAreaLog + Idoteid + CanopyHeight + DensityLog + 
          TempAnomWarm_June + MonthlyMeanTemp_June + 
          TidalHeightBinary + YearBinary +
            (1|Region) +(1|Meadow), 
        data=les5)
plot(predictorEffect("Idoteid", les_ido_1, partial.residuals=TRUE))

```

# Distributions
```{r histograms-prev}

dis2$Region <- ordered(dis2$Region, levels=c("AK", "BC", "WA", "OR", "BB", "SD"))
ggplot(dis2, aes(x=Epifauna, fill=Region))+geom_histogram(bins=15)

dis3$Region <- ordered(dis3$Region, levels=c("AK", "BC", "WA", "OR", "BB", "SD"))
ggplot(dis3, aes(x=Lacuna, fill=Region))+geom_histogram(bins=15)

dis4$Region <- ordered(dis4$Region, levels=c("AK", "BC", "WA", "OR", "BB", "SD"))
ggplot(dis4, aes(x=Ampithoid, fill=Region))+geom_histogram(bins=15)

dis_cc$Region <- ordered(dis_cc$Region, levels=c("AK", "BC", "WA", "OR", "BB", "SD"))
ggplot(dis_cc, aes(x=Epifauna, fill=Region))+geom_histogram(bins=15)

```

```{r histograms-les}

les2$Region <- ordered(les2$Region, levels=c("AK", "BC", "WA", "OR", "BB", "SD"))
ggplot(les2, aes(x=Epifauna, fill=Region))+geom_histogram(bins=15)

les3$Region <- ordered(les3$Region, levels=c("AK", "BC", "WA", "OR", "BB", "SD"))
ggplot(les3, aes(x=Lacuna, fill=Region))+geom_histogram(bins=15)

les4$Region <- ordered(les4$Region, levels=c("AK", "BC", "WA", "OR", "BB", "SD"))
ggplot(les4, aes(x=Ampithoid, fill=Region))+geom_histogram(bins=15)

les_cc$Region <- ordered(les_cc$Region, levels=c("AK", "BC", "WA", "OR", "BB", "SD"))
ggplot(les_cc, aes(x=Epifauna, fill=Region))+geom_histogram(bins=15)

```