---
title: "Community Interaction SEM results"
output: github_document
---

```{r setup, include=FALSE}
library(here)
source(here("R/helpers.R"))
source(here("R/coefs.R"))
library(nlme)
library(lme4)
library(dplyr)
library(readr)
library(DHARMa)
library(ggplot2)
library(GGally)
library(optimx)
library(performance)
library(piecewiseSEM)
library(effects)
library(ggeffects)
```

# SEMs comparing epifauna vs lacuna vs ampithoid vs iodteid vs richness

Try including epiphyte at the blade level. This variable was not important before, but I've changed the structure of the SEMs (two years only, meadow-scale predictors). And, the relationship with taxa might vary (haven't looked at that). Also, the data are now updated with better BB data.  

A few notes:  
 - Large epifauna only (except at BB).  
 - Epiphyte blades only. A handful are missing due to no epiphytes (wrong leaf etc)  
 - Zeros are included (not NAs), all sites for all models.  
 - Taxa abundances are log-transformed. 

```{r data}
# data ###
dis <- read_csv("data/epiphyte_SEM_data_all_large.csv")
# updating the SEM to compare the effects of using large vs all animals
dis$BladeAreaLog <- log10(dis$BladeArea)
dis$EpiphyteLog <- log10(dis$EpiphytePerAreamgcm2+0.01)
# use the full data set without subsetting because the SEM no longer includes epiphytes or grazing
dis1 <- select(dis, c(Epifauna = Epifauna_all, TempAnomWarm_June, MonthlyMeanTemp_June, CanopyHeight, 
                      DensityLog, YearBinary, Year, Meadow, Region,BladeAreaLog, TidalHeightBinary, 
                      Prevalence, LesionArea, EpiphytePerAreamgcm2, EpiphyteLog,
                      Lacuna = Lacuna_all, 
                      Ampithoid = Ampithoid_all, Idoteid = Idoteid_all, Richness = Richness_all))

dis1_large <- select(dis, c(Epifauna = Epifauna_large, TempAnomWarm_June, MonthlyMeanTemp_June, CanopyHeight, 
                      DensityLog, YearBinary, Year, Meadow, Region,BladeAreaLog, TidalHeightBinary, 
                      Prevalence, LesionArea, EpiphyteLog, Lacuna = Lacuna_large, 
                      Ampithoid = Ampithoid_large, Idoteid = Idoteid_large, Richness = Richness_large))
dis_large <- na.omit(dis1_large)
dis_large$Meadow_Year <- paste(dis_large$Meadow, dis_large$Year, sep = "_")
site_large <- distinct(dis_large, Meadow_Year, .keep_all = T)
site_large <- select(site_large, -c(Prevalence, LesionArea, EpiphyteLog, TidalHeightBinary, BladeAreaLog))
# site <- read_csv("data/epifauna_site_for_plotting.csv")
# site <- select(site, c())
```

## Prevalence + Epifauna

```{r prev1}
sem_prev_epi <- psem(
  lmer(Epifauna ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         CanopyHeight + DensityLog +
         YearBinary +
         (1|Meadow) + (1|Region),
       data=site_large),
  lmer(CanopyHeight ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=site_large),
  lmer(DensityLog ~ TempAnomWarm_June + MonthlyMeanTemp_June +
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=site_large),
    lmer(BladeAreaLog ~ Epifauna + CanopyHeight + DensityLog + 
         TempAnomWarm_June + MonthlyMeanTemp_June +
         TidalHeightBinary + YearBinary +
         (1|Region) + (1|Meadow),
       data=dis_large),
  lmer(EpiphyteLog ~ BladeAreaLog + Epifauna + CanopyHeight + DensityLog + 
         TempAnomWarm_June + MonthlyMeanTemp_June +
         TidalHeightBinary + YearBinary +
         (1|Region) + (1|Meadow),
       data=dis_large),
  glmer(Prevalence ~ BladeAreaLog + EpiphyteLog + 
          Epifauna + CanopyHeight + DensityLog + 
          TempAnomWarm_June + MonthlyMeanTemp_June + 
          TidalHeightBinary + YearBinary + 
          (1|Region) + (1|Meadow),
        data=dis_large,
        family = "binomial"),
  DensityLog%~~%CanopyHeight
)
summary(sem_prev_epi)

```

Passes global fit.  

Epifauna abundance is significant and positive predictor of prevalence.  

Coefficient table:  

```{r}
a <- coefs(sem_prev_epi)
knitr::kable(a, digits = 4)
```

## Prev + Amp
```{r prev2}
sem_prev_amp <- psem(
  lmer(Ampithoid ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         CanopyHeight + DensityLog +
         YearBinary +
         (1|Meadow) + (1|Region),
       data=site_large),
  lmer(CanopyHeight ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=site_large),
  lmer(DensityLog ~ TempAnomWarm_June + MonthlyMeanTemp_June +
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=site_large),
    lmer(BladeAreaLog ~ Ampithoid + CanopyHeight + DensityLog + 
         TempAnomWarm_June + MonthlyMeanTemp_June +
         TidalHeightBinary + YearBinary +
         (1|Region) + (1|Meadow),
       data=dis_large),
  lmer(EpiphyteLog ~ BladeAreaLog + Ampithoid + CanopyHeight + DensityLog + 
         TempAnomWarm_June + MonthlyMeanTemp_June +
         TidalHeightBinary + YearBinary +
         (1|Region) + (1|Meadow),
       data=dis_large),
  glmer(Prevalence ~ BladeAreaLog + EpiphyteLog + 
          Ampithoid + CanopyHeight + DensityLog + 
          TempAnomWarm_June + MonthlyMeanTemp_June + 
          TidalHeightBinary + YearBinary + 
          (1|Region) + (1|Meadow),
        data=dis_large,
        family = "binomial"),
  DensityLog%~~%CanopyHeight
)
summary(sem_prev_amp)

```


Passes global fit.  

Ampithoid abundance is not significant predictor of prevalence.  

Coefficient table:  
```{r}
b <- coefs(sem_prev_amp)
knitr::kable(b, digits = 4)

```


## Prev + Lac

```{r prev3}
sem_prev_lac <- psem(
  lmer(Lacuna ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         CanopyHeight + DensityLog +
         YearBinary +
         (1|Meadow) + (1|Region),
       data=site_large),
  lmer(CanopyHeight ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=site_large),
  lmer(DensityLog ~ TempAnomWarm_June + MonthlyMeanTemp_June +
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=site_large),
    lmer(BladeAreaLog ~ Lacuna + CanopyHeight + DensityLog + 
         TempAnomWarm_June + MonthlyMeanTemp_June +
         TidalHeightBinary + YearBinary +
         (1|Region) + (1|Meadow),
       data=dis_large),
  lmer(EpiphyteLog ~ BladeAreaLog + Lacuna + CanopyHeight + DensityLog + 
         TempAnomWarm_June + MonthlyMeanTemp_June +
         TidalHeightBinary + YearBinary +
         (1|Region) + (1|Meadow),
       data=dis_large),
  glmer(Prevalence ~ BladeAreaLog + EpiphyteLog + 
          Lacuna + CanopyHeight + DensityLog + 
          TempAnomWarm_June + MonthlyMeanTemp_June + 
          TidalHeightBinary + YearBinary + 
          (1|Region) + (1|Meadow),
        data=dis_large,
        family = "binomial"),
  DensityLog%~~%CanopyHeight
)
summary(sem_prev_lac)

```


Passes global fit.  

Lacuna abundance is significant and positive predictor of prevalence.  

Coefficient table:  
```{r}
c <- coefs(sem_prev_lac)
knitr::kable(c, digits = 4)

```

## Prev + Ido
```{r prev4}
sem_prev_ido <- psem(
  lmer(Idoteid ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         CanopyHeight + DensityLog +
         YearBinary +
         (1|Meadow) + (1|Region),
       data=site_large),
  lmer(CanopyHeight ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=site_large),
  lmer(DensityLog ~ TempAnomWarm_June + MonthlyMeanTemp_June +
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=site_large),
    lmer(BladeAreaLog ~ Idoteid + CanopyHeight + DensityLog + 
         TempAnomWarm_June + MonthlyMeanTemp_June +
         TidalHeightBinary + YearBinary +
         (1|Region) + (1|Meadow),
       data=dis_large),
  lmer(EpiphyteLog ~ BladeAreaLog + Idoteid + CanopyHeight + DensityLog + 
         TempAnomWarm_June + MonthlyMeanTemp_June +
         TidalHeightBinary + YearBinary +
         (1|Region) + (1|Meadow),
       data=dis_large),
  glmer(Prevalence ~ BladeAreaLog + EpiphyteLog + 
          Idoteid + CanopyHeight + DensityLog + 
          TempAnomWarm_June + MonthlyMeanTemp_June + 
          TidalHeightBinary + YearBinary + 
          (1|Region) + (1|Meadow),
        data=dis_large,
        family = "binomial"),
  DensityLog%~~%CanopyHeight
)
summary(sem_prev_ido)

```



Passes global fit.  

Idoteid abundance is not significant predictor of prevalence.  

Coefficient table:  
```{r}
d <- coefs(sem_prev_ido)
knitr::kable(d, digits = 4)

```

## Prev + Rich

```{r prev5}
sem_prev_rich <- psem(
  lmer(Richness ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         CanopyHeight + DensityLog +
         YearBinary +
         (1|Meadow) + (1|Region),
       data=site_large),
  lmer(CanopyHeight ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=site_large),
  lmer(DensityLog ~ TempAnomWarm_June + MonthlyMeanTemp_June +
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=site_large),
    lmer(BladeAreaLog ~ Richness + CanopyHeight + DensityLog + 
         TempAnomWarm_June + MonthlyMeanTemp_June +
         TidalHeightBinary + YearBinary +
         (1|Region) + (1|Meadow),
       data=dis_large),
  lmer(EpiphyteLog ~ BladeAreaLog + Richness + CanopyHeight + DensityLog + 
         TempAnomWarm_June + MonthlyMeanTemp_June +
         TidalHeightBinary + YearBinary +
         (1|Region) + (1|Meadow),
       data=dis_large),
  glmer(Prevalence ~ BladeAreaLog + EpiphyteLog + 
          Richness + CanopyHeight + DensityLog + 
          TempAnomWarm_June + MonthlyMeanTemp_June + 
          TidalHeightBinary + YearBinary + 
          (1|Region) + (1|Meadow),
        data=dis_large,
        family = "binomial"),
  DensityLog%~~%CanopyHeight
)
summary(sem_prev_rich)

```


Passes global fit.  

Epifauna richness is not significant predictor of prevalence.  

Coefficient table:  
```{r}
e <- coefs(sem_prev_rich)
knitr::kable(e, digits = 4)

```


## Lesion + Epifauna

```{r les_dat}
les_large <- subset(dis_large, LesionArea>0)
les_large$LesionAreaLog <- log10(les_large$LesionArea)
les_large <- na.omit(les_large)

site_les <- distinct(les_large, Meadow_Year, .keep_all = T)
```

```{r les_epi}
sem_les_epi <- psem(
  lmer(Epifauna ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         CanopyHeight + DensityLog +
         YearBinary +
         (1|Meadow) + (1|Region),
       data=site_les),
  lmer(CanopyHeight ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=site_les),
  lmer(DensityLog ~ TempAnomWarm_June + MonthlyMeanTemp_June +
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=site_les),
    lmer(BladeAreaLog ~ Epifauna + CanopyHeight + DensityLog + 
         TempAnomWarm_June + MonthlyMeanTemp_June +
         TidalHeightBinary + YearBinary +
         (1|Region) + (1|Meadow),
       data=les_large),
  lmer(EpiphyteLog ~ BladeAreaLog + Epifauna + CanopyHeight + DensityLog + 
          TempAnomWarm_June + MonthlyMeanTemp_June + 
          TidalHeightBinary + YearBinary + 
          (1|Region) + (1|Meadow),
        data=les_large),
  lmer(LesionAreaLog ~ BladeAreaLog + EpiphyteLog + Epifauna + CanopyHeight + DensityLog + 
          TempAnomWarm_June + MonthlyMeanTemp_June + 
          TidalHeightBinary + YearBinary + 
          (1|Region) + (1|Meadow),
        data=les_large),
  DensityLog%~~%CanopyHeight
)
summary(sem_les_epi)
```


Passes global fit.  

Epifauna abundance is significant and positive predictor of lesion area  

Coefficient table:  

```{r}
f <- coefs(sem_les_epi)
knitr::kable(f, digits = 4)

```

## Lesion + Amp

```{r les_amp}
sem_les_amp <- psem(
  lmer(Ampithoid ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         CanopyHeight + DensityLog +
         YearBinary +
         (1|Meadow) + (1|Region),
       data=site_les),
  lmer(CanopyHeight ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=site_les),
  lmer(DensityLog ~ TempAnomWarm_June + MonthlyMeanTemp_June +
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=site_les),
    lmer(BladeAreaLog ~ Ampithoid + CanopyHeight + DensityLog + 
         TempAnomWarm_June + MonthlyMeanTemp_June +
         TidalHeightBinary + YearBinary +
         (1|Region) + (1|Meadow),
       data=les_large),
  # lmer(EpiphyteLog ~ BladeAreaLog + Ampithoid + CanopyHeight + DensityLog + 
  #         TempAnomWarm_June + MonthlyMeanTemp_June + 
  #         TidalHeightBinary + YearBinary + 
  #         (1|Region) + (1|Meadow),
  #       data=les_large),
  lmer(LesionAreaLog ~ BladeAreaLog + #EpiphyteLog + 
         Ampithoid + CanopyHeight + DensityLog + 
          TempAnomWarm_June + MonthlyMeanTemp_June + 
          TidalHeightBinary + YearBinary + 
          (1|Region) + (1|Meadow),
        data=les_large),
  DensityLog%~~%CanopyHeight
)
summary(sem_les_amp)
```



Passes global fit.  

Ampithoid abundance is not significant predictor of lesion area (but negative pattern).    

Coefficient table:  

```{r}
g <- coefs(sem_les_amp)
knitr::kable(g, digits = 4)

```

## Lesion + Lac

```{r les_lac}
sem_les_lac <- psem(
  lmer(Lacuna ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         CanopyHeight + DensityLog +
         YearBinary +
         (1|Meadow) + (1|Region),
       data=site_les),
  lmer(CanopyHeight ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=site_les),
  lmer(DensityLog ~ TempAnomWarm_June + MonthlyMeanTemp_June +
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=site_les),
    lmer(BladeAreaLog ~ Lacuna + CanopyHeight + DensityLog + 
         TempAnomWarm_June + MonthlyMeanTemp_June +
         TidalHeightBinary + YearBinary +
         (1|Region) + (1|Meadow),
       data=les_large),
  lmer(EpiphyteLog ~ BladeAreaLog + Lacuna + CanopyHeight + DensityLog + 
          TempAnomWarm_June + MonthlyMeanTemp_June + 
          TidalHeightBinary + YearBinary + 
          (1|Region) + (1|Meadow),
        data=les_large),
  lmer(LesionAreaLog ~ BladeAreaLog + EpiphyteLog + Lacuna + CanopyHeight + DensityLog + 
          TempAnomWarm_June + MonthlyMeanTemp_June + 
          TidalHeightBinary + YearBinary + 
          (1|Region) + (1|Meadow),
        data=les_large),
  DensityLog%~~%CanopyHeight
)
summary(sem_les_lac)
```



Passes global fit.  

Lacuna abundance is significant and positive predictor of leison area.    

Coefficient table:  

```{r}
h <- coefs(sem_les_lac)
knitr::kable(h, digits = 4)

```

## Lesion + Ido

```{r les_ido}
sem_les_ido <- psem(
  lmer(Idoteid ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         CanopyHeight + DensityLog +
         YearBinary +
         (1|Meadow) + (1|Region),
       data=site_les),
  lmer(CanopyHeight ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=site_les),
  lmer(DensityLog ~ TempAnomWarm_June + MonthlyMeanTemp_June +
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=site_les),
    lmer(BladeAreaLog ~ Idoteid + CanopyHeight + DensityLog + 
         TempAnomWarm_June + MonthlyMeanTemp_June +
         TidalHeightBinary + YearBinary +
         (1|Region) + (1|Meadow),
       data=les_large),
  lmer(EpiphyteLog ~ BladeAreaLog + Idoteid + CanopyHeight + DensityLog + 
          TempAnomWarm_June + MonthlyMeanTemp_June + 
          TidalHeightBinary + YearBinary + 
          (1|Region) + (1|Meadow),
        data=les_large),
  lmer(LesionAreaLog ~ BladeAreaLog + EpiphyteLog + Idoteid + CanopyHeight + DensityLog + 
          TempAnomWarm_June + MonthlyMeanTemp_June + 
          TidalHeightBinary + YearBinary + 
          (1|Region) + (1|Meadow),
        data=les_large),
  DensityLog%~~%CanopyHeight
)
summary(sem_les_ido)
```


Passes global fit.  

Idoteid abundance is significant and positive predictor of lesion area.    

Coefficient table:  

```{r}
i <- coefs(sem_les_ido)
knitr::kable(i, digits = 4)

```

## Lesion + Rich

```{r les_rich}
sem_les_rich <- psem(
  lmer(Richness ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         CanopyHeight + DensityLog +
         YearBinary +
         (1|Meadow) + (1|Region),
       data=site_les),
  lmer(CanopyHeight ~ TempAnomWarm_June + MonthlyMeanTemp_June + 
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=site_les),
  lmer(DensityLog ~ TempAnomWarm_June + MonthlyMeanTemp_June +
         YearBinary + 
         (1|Meadow) + (1|Region),
       data=site_les),
    lmer(BladeAreaLog ~ Richness + CanopyHeight + DensityLog + 
         TempAnomWarm_June + MonthlyMeanTemp_June +
         TidalHeightBinary + YearBinary +
         (1|Region) + (1|Meadow),
       data=les_large),
  lmer(EpiphyteLog ~ BladeAreaLog + Richness + CanopyHeight + DensityLog + 
          TempAnomWarm_June + MonthlyMeanTemp_June + 
          TidalHeightBinary + YearBinary + 
          (1|Region) + (1|Meadow),
        data=les_large),
  lmer(LesionAreaLog ~ BladeAreaLog + EpiphyteLog + Richness + CanopyHeight + DensityLog + 
          TempAnomWarm_June + MonthlyMeanTemp_June + 
          TidalHeightBinary + YearBinary + 
          (1|Region) + (1|Meadow),
        data=les_large),
  DensityLog%~~%CanopyHeight
)
summary(sem_les_rich)
```


Passes global fit.  

Epifauna richness is not significant predictor of lesion area.    

Coefficient table:  

```{r}
j <- coefs(sem_les_rich)
knitr::kable(j, digits = 4)

```

## Partial coefficients

### prevalence

```{r}
prev_epi_1 <- glmer(Prevalence ~ BladeAreaLog + EpiphyteLog + Epifauna + CanopyHeight + DensityLog + 
          TempAnomWarm_June + MonthlyMeanTemp_June + 
          TidalHeightBinary + YearBinary +
            (1|Region) +(1|Meadow), 
        data=dis_large,
        family="binomial")
plot(predictorEffect("Epifauna", prev_epi_1, partial.residuals=T))
# will want to try and get the year/site means plotted onto this plot, but can hold off for now?
prev_lac_1 <- glmer(Prevalence ~ BladeAreaLog + EpiphyteLog + Lacuna + CanopyHeight + DensityLog + 
          TempAnomWarm_June + MonthlyMeanTemp_June + 
          TidalHeightBinary + YearBinary +
            (1|Region) +(1|Meadow), 
        data=dis_large,
        family="binomial")
plot(predictorEffect("Lacuna", prev_lac_1, partial.residuals=T))

prev_amp_1 <- glmer(Prevalence ~ BladeAreaLog + EpiphyteLog + Ampithoid + CanopyHeight + DensityLog + 
          TempAnomWarm_June + MonthlyMeanTemp_June + 
          TidalHeightBinary + YearBinary +
            (1|Region) +(1|Meadow), 
        data=dis_large,
        family="binomial")
plot(predictorEffect("Ampithoid", prev_amp_1,partial.residuals=TRUE))

prev_ido_1 <- glmer(Prevalence ~ BladeAreaLog + EpiphyteLog + Idoteid + CanopyHeight + DensityLog + 
          TempAnomWarm_June + MonthlyMeanTemp_June + 
          TidalHeightBinary + YearBinary +
            (1|Region) +(1|Meadow), 
        data=dis_large,
        family="binomial")

plot(predictorEffect("Idoteid", prev_ido_1,partial.residuals=T))

prev_rich_1 <- glmer(Prevalence ~ BladeAreaLog + EpiphyteLog + Richness + CanopyHeight + DensityLog + 
          TempAnomWarm_June + MonthlyMeanTemp_June + 
          TidalHeightBinary + YearBinary +
            (1|Region) +(1|Meadow), 
        data=dis_large,
        family="binomial")
plot(predictorEffect("Richness", prev_rich_1,partial.residuals=TRUE, main="type='link'"))

```

### lesion

```{r}

les_epi_1 <- lmer(LesionAreaLog ~ BladeAreaLog + EpiphyteLog + Epifauna + CanopyHeight + DensityLog + 
          TempAnomWarm_June + MonthlyMeanTemp_June + 
          TidalHeightBinary + YearBinary +
            (1|Region) +(1|Meadow), 
        data=les_large)
plot(predictorEffect("Epifauna", les_epi_1, partial.residuals=TRUE))


les_lac_1 <- lmer(LesionAreaLog ~ BladeAreaLog + EpiphyteLog + Lacuna + CanopyHeight + DensityLog + 
          TempAnomWarm_June + MonthlyMeanTemp_June + 
          TidalHeightBinary + YearBinary +
            (1|Region) +(1|Meadow), 
        data=les_large)
plot(predictorEffect("Lacuna", les_lac_1, partial.residuals=TRUE))


les_amp_1 <- lmer(LesionAreaLog ~ BladeAreaLog + EpiphyteLog + Ampithoid + CanopyHeight + DensityLog + 
          TempAnomWarm_June + MonthlyMeanTemp_June + 
          TidalHeightBinary + YearBinary +
            (1|Region) +(1|Meadow), 
        data=les_large)
plot(predictorEffect("Ampithoid", les_amp_1, partial.residuals=TRUE))


les_ido_1 <- lmer(LesionAreaLog ~ BladeAreaLog + EpiphyteLog + Idoteid + CanopyHeight + DensityLog + 
          TempAnomWarm_June + MonthlyMeanTemp_June + 
          TidalHeightBinary + YearBinary +
            (1|Region) +(1|Meadow), 
        data=les_large)
plot(predictorEffect("Idoteid", les_ido_1, partial.residuals=TRUE))
  

les_rich_1 <- lmer(LesionAreaLog ~ BladeAreaLog + EpiphyteLog + Richness + CanopyHeight + DensityLog + 
          TempAnomWarm_June + MonthlyMeanTemp_June + 
          TidalHeightBinary + YearBinary +
            (1|Region) +(1|Meadow), 
        data=les_large)
plot(predictorEffect("Richness", les_rich_1, partial.residuals=T, type="rescale"))
# plot(ggpredict(les_rich_1, terms = "Richness"), rawdata = TRUE, labels = scales::log10_trans())

```

